### 2013-07-06 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding parallel verification data

%%---------------------------------------------------------------------------%%
\section{Parallel MCSA Verification\ }
\label{sec:parallel_verification}
Before we consider the parallel performance of the MCSA algorithm, we
must first verify that the algorithm generates the correct solution in
parallel with respect to reference solutions provided by production
Krylov methods.

>>>>

%%---------------------------------------------------------------------------%%
\section{Parallel MCSA Verification\ }
\label{sec:parallel_verification}
Before we consider the parallel performance of the MCSA algorithm, we
must first verify that the algorithm generates the correct solution in
parallel with respect to reference solutions provided by production
Krylov methods. To verify correctness, we use solutions the neutron
diffusion system presented in
Appendix~\ref{chap:diffusion_problem}. As the reference computation,
serial results will be used from the conjugate gradient solver in
Belos, a linear solvers package in the Trilinos scientific computing
libraries \citep{heroux_overview_2005}. In identical fashion to the
verification for the $SP_N$ equations performed in
\S~\ref{sec:spn_mcsa_verification}, we will solve the neutron
diffusion problem in parallel using multiple cores on a desktop
machine. For each parallel solution, the solution at each grid point
in the system will be compared to the solution at the same grid point
in the serial reference case with the minimum and maxiumum absolute
differences of these values reported.

GMRES and conjugate gradient solvers from the Belos package were used
on 4 cores as a means of both assuring the Krylov solvers produce the
same results on multiple cores and as a means of providing an
acceptable range of minimum and maximum values in the comparison. For
MCSA, a range of MSOD parameters will be used such that problems with
multiple sets and multiple blocks may be tested along with
overlap. When multiple sets were leveraged, a single history was used
to compute the MCSA correction for every DOF in the problem. For all
solvers, the flux was converged to a tolerance of \sn{1}{-8} and
therefore if the comparisons agree within this tolerance the solutions
will be deemed
correct. Table~\ref{tab:parallel_verification_parameters} gives the
parameters for the verification problem and
Table~\ref{tab:parallel_mcsa_verification} gives the results of the
calculations. Solver parameters used for MCSA are given in
Table~\ref{tab:parallel_mcsa_parameters}.

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      $dx$ & 0.1 \\
      $dy$ & 0.1 \\
      $N_x$ & 400 \\
      $N_y$ & 400 \\
      $N$ & 160,000 \\
      $\Sigma_a$ & 5.0 \\
      $\Sigma_s$ & 1.0 \\
      Boundary Type & Vacuum \\
      Linear Solver Tolerance & \sn{1}{-8} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parallel MCSA verification model problem parameters.}
    \textit{The neutron diffusion equation in 2 dimensions is used for
      the model problem.}}
  \label{tab:parallel_verification_parameters}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lc}\hline\hline
      \multicolumn{1}{l}{Parameter}& 
      \multicolumn{1}{c}{Value}\\\hline
      Histories & 1 per DOF \\
      Weight Cutoff & \sn{1}{-2} \\
      Fixed Point & Richardson \\
      Estimator & Collision \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parallel MCSA verification solver parameters.}}
  \label{tab:parallel_mcsa_parameters}
\end{table}

\begin{table}[h!]
  \begin{center}
    \begin{tabular}{lccccll}\hline\hline
      \multicolumn{1}{l}{Solver}& 
      \multicolumn{1}{c}{Blocks}& 
      \multicolumn{1}{c}{Sets}& 
      \multicolumn{1}{c}{Cores}& 
      \multicolumn{1}{c}{Overlap}& 
      \multicolumn{1}{l}{Min Difference}& 
      \multicolumn{1}{l}{Max Difference}\\\hline
      Conjugate Gradient & - & - & 4 & - & 0.0 & \sn{1.11022}{-16} \\
      GMRES & - & - & 4 & - & \sn{5.64215}{-13} & \sn{3.83348}{-9} \\
      MCSA & 2 & 1 & 2 & 0 & \sn{8.60423}{-16} & \sn{7.6806}{-9} \\
      MCSA & 3 & 1 & 3 & 0 & \sn{6.41154}{-15} & \sn{7.65397}{-9} \\
      MCSA & 4 & 1 & 4 & 0 & \sn{2.66454}{-15} & \sn{7.62623}{-9} \\
      MCSA & 2 & 2 & 4 & 0 & \sn{1.52656}{-15} & \sn{7.57108}{-9} \\
      MCSA & 1 & 4 & 4 & 0 & \sn{5.55112}{-16} & \sn{7.61631}{-9} \\
      MCSA & 8 & 1 & 8 & 0 & \sn{6.13398}{-15} & \sn{7.51744}{-9} \\
      MCSA & 4 & 2 & 8 & 0 & \sn{1.03251}{-14} & \sn{7.62601}{-9} \\
      MCSA & 2 & 4 & 8 & 0 & \sn{5.13478}{-15} & \sn{7.60777}{-9} \\
      MCSA & 1 & 8 & 8 & 0 & \sn{1.80411}{-15} & \sn{7.60651}{-9} \\
      MCSA & 2 & 1 & 2 & 5 & \sn{2.47025}{-15} & \sn{7.58882}{-9} \\
      MCSA & 3 & 1 & 3 & 5 & \sn{2.44249}{-15} & \sn{7.6326}{-9} \\
      MCSA & 4 & 1 & 4 & 5 & \sn{7.49401}{-16} & \sn{7.49014}{-9} \\
      MCSA & 2 & 2 & 4 & 5 & \sn{1.19349}{-15} & \sn{7.61814}{-9} \\
      MCSA & 1 & 4 & 4 & 5 & \sn{5.55112}{-16} & \sn{7.61631}{-9} \\
      MCSA & 8 & 1 & 8 & 5 & \sn{2.05391}{-15} & \sn{7.63955}{-9} \\
      MCSA & 4 & 2 & 8 & 5 & \sn{9.57567}{-15} & \sn{7.61313}{-9} \\
      MCSA & 2 & 4 & 8 & 5 & \sn{5.7454}{-15} & \sn{7.60767}{-9} \\
      MCSA & 1 & 8 & 8 & 5 & \sn{1.80411}{-15} & \sn{7.60651}{-9} \\
      MCSA & 2 & 1 & 2 & 10 & \sn{1.08247}{-15} & \sn{7.63231}{-9} \\
      MCSA & 3 & 1 & 3 & 10 & \sn{3.27516}{-15} & \sn{7.60211}{-9} \\
      MCSA & 4 & 1 & 4 & 10 & \sn{4.996}{-16} & \sn{7.64756}{-9} \\
      MCSA & 2 & 2 & 4 & 10 & \sn{4.13558}{-15} & \sn{7.60259}{-9} \\
      MCSA & 1 & 4 & 4 & 10 & \sn{5.55112}{-16} & \sn{7.61631}{-9} \\
      MCSA & 8 & 1 & 8 & 10 & \sn{9.71445}{-16} & \sn{7.58535}{-9} \\
      MCSA & 4 & 2 & 8 & 10 & \sn{7.77156}{-16} & \sn{7.65978}{-9} \\
      MCSA & 2 & 4 & 8 & 10 & \sn{4.16334}{-16} & \sn{7.63191}{-9} \\
      MCSA & 1 & 8 & 8 & 10 & \sn{1.80411}{-15} & \sn{7.60651}{-9} \\
      %%
      \hline\hline
    \end{tabular}
  \end{center}
  \caption{\textbf{Parallel MCSA verification results.}
    \textit{Difference values given are absolute values. The neutron
      diffusion equation in 2 dimensions is used for the model problem
      with the parameters given in
      Table~\ref{tab:parallel_verification_parameters}. A serial
      conjugate gradient calculation is used as the reference
      computation and neutron fluxes are compared
      element-wise. Parameters used for the MCSA solver are given in
      Table~\ref{tab:parallel_mcsa_parameters}. All solvers including
      the reference computation were converged to tolerance of
      \sn{1}{-8}.}}
  \label{tab:parallel_mcsa_verification}
\end{table}

From the data we see that for all solvers, the parallel results agree
within the solution tolerance of the reference serial results for all
DOF in the system. In addition, we do not notice any systematic
differences in the results as a function of number of blocks, number
of sets, or amount of overlap. In addition, the parallel GMRES results
have maximum absolute differences of the same magnitude as all MCSA
results and a larger minimum absolute difference than all MCSA results
by three orders of magnitude. Based on these results, MCSA parallized
with an MSOD, and in particular the implementation used here,
generates the correct results with respect to the serial conjugate
gradient reference computation.
